Acid-induced protein gels: from gelation to stress-induced failure

### 2015-10-26 talk_Montpellier.tex
critical vs super-critical gel story
conclusion of over-acidification

\begin{frame}{Acidifying casein solutions with \textup{HCl}}
\tikzsetnextfilename{dosage}
\input{fig_presentation/dosage.pgf}
\end{frame}

\begin{frame}{Over-acidified protein gels: beyond isoelectric pH}
	\tikzsetnextfilename{prise_cas4}
	\input{fig_soundbite_palavas/prise_cas4.pgf}
	\begin{itemize}
	\item[$\Rightarrow$] still solid
	\end{itemize}
\end{frame}

\begin{frame}{Linear rheology, from power-law to soft glassy}
	\tikzsetnextfilename{sweep_cas4}
	\input{fig_soundbite_palavas/sweep_cas4.pgf}
	\begin{itemize}
	\item Near isoelectric, power law rheology $G^\prime, G^{\prime\prime}$ typical of gels 
	\item Over-acidification lowers exponent and creates a minimum in $G^{\prime\prime}$
	\item Transition to soft-glassy behaviour \\\textit{\footnotesize Sollich, PRE (1998); Mason, Curr. Opin. Colloid Interface Sci. (1999)}
	\end{itemize}
\end{frame}

@@

>>>>

\begin{frame}{Over-acidified protein gels: beyond isoelectric pH}
	\tikzsetnextfilename{prise_cas4}
	\input{fig_soundbite_palavas/prise_cas4.pgf}
	\begin{itemize}
	\item[$\Rightarrow$] still solid
	\item From critical to super-critical gels?
	\end{itemize}
\end{frame}

\begin{frame}{Linear rheology, from power-law to soft glassy}
	\tikzsetnextfilename{sweep_cas4}
	\input{fig_soundbite_palavas/sweep_cas4.pgf}
	\begin{itemize}
	\item Near isoelectric, power law rheology $G^\prime, G^{\prime\prime}$ typical of critical gels 
	\item Over-acidification lowers exponent and creates a minimum in $G^{\prime\prime}$
	\item Transition to soft-glassy behaviour \\\textit{\footnotesize Sollich, PRE (1998); Mason, Curr. Opin. Colloid Interface Sci. (1999)}
	\end{itemize}
\end{frame}

@@

\begin{frame}{Over-acidification summary}
\begin{itemize}
\item The critical network is still there but over-compressed
\item Transition to soft glassy rheology
\item Creep regimes 1 and 2 still valid but messy in the middle
\item[$\Rightarrow$] Rupture scenario of critical gel only partially valid for other gels.
\end{itemize}
\end{frame}
